\hypertarget{index_Introduction}{}\section{Introduction}\label{index_Introduction}
The source directories Radau5-\/\-N\-G, Rock4-\/\-N\-G, Rock4-\/\-L, Rodas-\/\-N\-G, S\-D\-I\-R\-K\-L and Symplectic\-R\-K contains sources of different Runge-\/\-Kutta methods written in C++.

\begin{quotation}
{\bfseries  Radau5-\/\-N\-G } is a rewritting of Hairer and Wanner code, optimized, but with some

\end{quotation}
restrictions (see documentation).

\begin{quotation}
{\bfseries  Rock4-\/\-N\-G } is a rewritting of A. Abdulle code, avoiding vector copies.

\end{quotation}


\begin{quotation}
{\bfseries  Rock4-\/\-L } is an adaptation of Rock4 method ro linear (actually affine)

\end{quotation}
problems $ du/dt= A u +B.$, with $ A $ linear and $ B $ independent of $ t.$

\begin{quotation}
{\bfseries  Rodas-\/\-N\-G } is a rewritting of Hairer and Wanner code, optimized, but with some

\end{quotation}
restrictions (see documentation).

\begin{quotation}
{\bfseries  S\-D\-I\-R\-K\-L} is a generic implementation of S\-D\-I\-R\-K methods in the linear (affine) case. Thus, linear systems must be solved.

\end{quotation}


\begin{quotation}
{\bfseries  Symplectic\-R\-K} is the (the family of) symplectic Gauss methods.

\end{quotation}


See documentation of individual programs.\hypertarget{index_General}{}\section{General considerations about implementation.}\label{index_General}
All is written in C++, and some program must be used with recent compilers (c++-\/11 norm). Everuthing has been tested with g++, icc and clang compilers.

This is a library of templates, no intermediate binary is created.

For all these programs, a class must be created wich describes the program to be solved.\hypertarget{index_Directory}{}\subsection{Directory structure\-:}\label{index_Directory}
\begin{quotation}
{\bfseries  common/include} contains all the classes, methods and functions common to the different programs.

\end{quotation}


\begin{quotation}
for each program, the corresponding directory contains an {\bfseries include} directory, which stores the different classes of the program and {\bfseries test} directories.

\end{quotation}
\hypertarget{index_test}{}\subsubsection{Test directories\-:}\label{index_test}
Each {\bfseries  test} directory contains a main program, all the necessary classes, and a cmake file. To compile and test the program\-:

\begin{quotation}
Adapt C\-Make file if necessary.

\end{quotation}


\begin{quotation}
{\bfseries cd Build} directory

\end{quotation}


\begin{quotation}
{\bfseries cmake ..} (possibly with an option to determine the compiler you want to use); see the Cmake files provided.

\end{quotation}


\begin{quotation}
{\bfseries  make} a {\bfseries  ./run } file is created.

\end{quotation}


\begin{quotation}
{\bfseries run} to execute the program. \end{quotation}
